Catchy Title Goes Here

### 2018-06-21 Paper/paper.tex
updated discussion text

A second set of assumptions arise from the inherent limitations of surveillance and survey data.

Applications -- design of sero surveys.

Periodic assessment of sero-prevalence.

>>>>

A second set of assumptions arise from the inherent limitations of surveillance and survey data. As highlighted in the definition of the vaccination effectiveness parameter, $\gamma$, vaccination surveys often rely on maternal recall, which is frequently non-specific and may suffer from recall bias.  This results in the indeterminacy of the vaccination effectivenes parameter as a measure of field effectiveness of the vaccine or the reliability of vaccine survey responses. In the specific case of measles, there are multiple potential sources of vaccination -- routine immunizations and multiple types of supplemental activities that range from child-maternal health days to SIAs to outbreak response vaccination campaigns. The vaccination hazard estimated here is not specific to any of these because the vaccintion question in the DHS survey is not specific to any one source of vacciantion (REF - Takahashi).  Thus, the vaccination hazard reflects the sum of all sources of vaccination. The age-specific case surveillance reflects only those cases that were recorded in the health system and may contain biases if, for example, younger children are more likely to be taken to clinics or hositapls because of more severe disease.

Though comprehensive serological surveys remain the gold-standard for estimating the age-distribution of immunity, our analysis suggests that reasonable estimates of seroprevalence may be possible by combining vaccination coverage surveys and routinely collected age-specific case reports.  In particular, this may allow initial estimates of seroprevalence that could be used to support the design of serological surveys.  Further, these methods would permit evaluation of population immunity in years when sero-surveys are not available.  As illustrated in the simulation experiment, the combination of limited serological surveys, here only 6-59 months of age, with routine surveillance data may allow robust estimates of population immunity and evaluation of vaccination program performance, through the vaccination effectiveness parameter.  Thus, by combining serological surveys with existing surveillance data, it may be possible to obtain operationally useful estimates using smaller and less expensive survey designs.  The development of optimal survey designs (age ranges and sample sizes) to estimate population immunity by combining sero surveys with surveillence is a useful avenue for future research.
